Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-08-30 paper/uist_2016/paper.tex
grammatical changes; added some references; updated pictures; tbc

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by ***(Neel Joshi's and Johannes Kopf's work from Microsoft)****, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimentional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party Javascript libraries, and therefore does not transfer sensitive user data nor store it.

@@

\subsubsection{Hyperlapse Creation} 
The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route. Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes. To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification. Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation. (need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup. (need to expand too)
-- to be continued

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-time_of_day}
     \caption{Brightness of Rewind images are manipulated in order to mimic the time of day that the trip took place.}
     \label{fig:timeofday}
\end{figure}

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-seasons}
     \caption{Saturation of Rewind images are manipulated in order to mimic the season that the trip took place.}
     \label{fig:season}
\end{figure}

>>>>

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by \cite{kopf2014firstperson, joshi2015realtime}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.

@@

\subsubsection{Hyperlapse Creation} 
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser. Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incorporate a large training dataset into the rendering pipeline. Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

As the Google Street view images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex. the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times). Thus sky and ground regions could be approximated by generalizing the observed geographical information of the incoming images. Each pixel was first converted from RGB representation into HSV color space. For seasonal changes, a range of HSV values was estimated for plantation classification and those HSV values that fell within the range were adjusted for desired seasonal effects. Each HSV value was then converted back to RGB color space for JavaScript canvas painting (Figure~\ref{fig:season}). Similarly, for creating nightly effects such as sunset and evening scenes, sky colors were modified using the same technique. In addition, two linear brightness and saturation filters were applied locally and globally (Figure~\ref{fig:timeofday}). As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1. Approximated sky region 2. Non-sky region in the approximated sky region 3. Approximated Ground region. RGB values of each pixel were down-scaled based on the region the pixel is classified in.

For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (currently only available for images from [anonymized: our state/province]). Sky colors was adjusted again using the technique mentioned previously for overcast, rainy and snowy sky. For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the hyperlapse and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}).

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-seasons2}
     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
     \label{fig:season}
\end{figure}

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-time_of_day2}
     \caption{Per-pixel change is applied based on classified region}
     \label{fig:timeofday}
\end{figure}

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-weather}
     \caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
     \label{fig:weather}
\end{figure}
